---
title: "Stork net - Labeled images"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

library(tidyverse)
library(lubridate)
library(here)
```

```{r read_data}
files_2019_sampled_labeled <-
  read_csv(here("images", "files_2019_sampled_labeled.csv")) %>%
  mutate(date = dmy(date))
```


## Plotting overall numbers

### Class imbalance?
Is there any class imbalance? Categories 0 to 2 are about equal, but notably less in 3. We'll see if this is an issue.

```{r overall}

files_2019_sampled_labeled %>%
  ggplot(aes(x = stork_number)) +
  geom_bar()

```

### Trend over time?
Is there a structure of stork number over time? As expected, there is.

```{r}
files_2019_sampled_labeled %>%
  ggplot(aes(x = date)) +
  geom_histogram() +
  facet_grid(stork_number~.)
```


### Trend over time-of-day?
At what time are how many storks present? There's some structure, but consider that this is the sum over all dates.

```{r}
files_2019_sampled_labeled %>%
  ggplot(aes(x = time)) +
  geom_histogram() +
  facet_grid(stork_number~.)
```

